### 2013-05-31 doc/nips2013/abstract.tex
added pdf figures

\begin{abstract}
Latent-variable models.
\end{abstract}

>>>>

\begin{abstract}
Parameter estimation in log-linear latent-variable models is typically
performed using local optimization, which is prone to local optima.
In this paper,
%we show how to leverage recent advances in the method of moments
%to alleviate these problems.
we leverage recent advances in the method of moments to estimate latent
moments of the target distribution,
which we incorporate as constraints on the original optimization
problem.
In favorable cases, these constraints provide full information and render the
original optimization problem
convex; in other cases, the constraints offer partial information,
but still provide significant aid to the original optimization problem.
Factorial models do require special attention,
so we develop a new unshuffling factorization technique to induce
constraints for these models.
Empirically, we show that our methods provide substantial gains
across several models.
\end{abstract}
